# (PART) PovcalNet Update {.unnumbered}

# Introduction to PovcalNet Update {#intro-povcal}

Updating the PovcalNet system requires putting together many different pieces
that interact with each other. This part of the book is divided from the
perspective of independent procedures rather than particular outputs. For
instance, the **Master file** is a single Excel file with several spreadsheets
that is updated in several processes. Instead of creating a chapter for updating
the whole Master file (though it exists as a summary), we think it is better to
explain separately each of the processes that add up to update the whole Master
file.

## Overview {#update-overview .unnumbered}

The chart below summarizes the PovcalNet update process. As you can see, the
different components of the process interact with each other in such a way that
updating one of them will most like require to update some of the others. For
instance, the master file is updated when either one of the auxiliary data is
updated or the .PCB-files process is executed. In addition, it is necessary to
upload master data into the Data Management System to make sure everything is up
to date. Also, keep in mind that the visualization below is just a
simplification of the whole process, in which each of the nodes of the chart is
a process in itself.

You can click on each of the nodes of the charts to easily identify which nodes
are affected by modifying the selected node. Hovering over the nodes produces a
similar effect.

```{r nodes-overview, echo=FALSE}
library(tidyverse)
library(visNetwork)
nodes <- tibble(
  label = c(
    "Datalibweb",
    "WDI",
    "Other Sources",
    "Auxiliary data", 
    "LIS Data", 
    "Group Data",
    "Microdata",
    "Master file",
    "PCN files process",
    ".PCP files",
    "Upload to DM", 
    "txt from LIS"
  ), 
  level = c(1, 1, 1, 2, 2, 2, 2, 3, 4, 5, 6, -1)
  # , 
  # shape = c(
  #   rep("square", 3),
  #   rep("circle", 4)
  # ),
  # group c(
  #   ""
  # )
)

nodes <- nodes %>% 
  mutate(id =  row_number())

edges <- tibble(from   = c(1, 1, 1, 2, 3, 4, 4, 5, 6 , 7,  8,  9, 10, 10, 12), 
                to     = c(4, 7, 5, 4, 4, 8, 9, 9, 10, 9, 11, 10, 8,  11, 1))
```

```{r vis-overview, echo=FALSE}
visNetwork(nodes, edges, height = "500px", width = "100%") %>% 
  visNodes(color = list(background = "lightblue", 
                        border = "darkblue",
                        highlight = "yellow"),
           shadow = list(enabled = TRUE, size = 10)) %>%
  visEdges(arrows =list(to = list(enabled = TRUE, 
                                  scaleFactor = 1))) %>% 
  visOptions(highlightNearest =  list(enabled = T, 
                                      # degree = 2, 
                                      hover = T),
             nodesIdSelection = TRUE
             ) %>%
  visHierarchicalLayout(direction = "LR", 
                        levelSeparation = 100)
  
```
