# Create .PCB files

As explained in the [introduction](#intro-povcal) of this part of the book,
creating the .PCB files are the last step of the process before uploading
everything to the PovcalNet system. The .PCB files are... (**TO-DO: Ask Tony to
provide his inputs for the explanations.**)

## The povcalnet\_update repository

Once you have updated all the sheets in the master file--besides the
"SurveyMean" sheet--and have updated the microdata in the P drive, the next step
is to create the .pcb files and update the "SurveyMean" sheet. All of this is
done with the
[PovcalNet-Team/povcalnet\_update](https://github.com/PovcalNet-Team/povcalnet_update)
repository. Make sure you clone the repo and open it as a [project in
Rstudio](https://martinctc.github.io/blog/rstudio-projects-and-working-directories-a-beginner's-guide/).
You will find the project has three .R files only. If everything goes as
expected, you'll only need to use the file *00.master.R*.

In rare cases, you will need to modify the functions in other two files. The
*utils.R* file has generic functions such as loading the master file into the
system, or creating survey IDs. These functions are used all along the process.
The *process\_functions.R* file contain functions for specific parts of the
projects are executed usually once along the whole process. Basically, the
*00.master.R* calls these functions in order in the same way that a master
do-file call other do-files that do specific things.

In this chapter, we break down the *00.master.R* file, so you understand how to
run it, the logic behind, and what to do in case it needs to be fixed. Let's
start by installing the minimum necessary packages. *00.master.R* file assumes
you already have them installed, so you should run the code below before you
start.

```{r, eval = FALSE}
# pkg_load <- knitr::combine_words(pkgs, before = "`")
pkgs <- c("janitor", "data.table", "tidyverse", "writexl", "readxl", "here", "devtools")
no_installed <- pkgs[!(pkgs  %in%  installed.packages())]
installed.packages(no_installed)
```

## Generate the .pcb files

### Directories

The first section includes the directories in which you're going to be working.
As of today (2020-11-20), the `datadir` directory is for `2020_JUL` as it was
the last release of PovcalNet. However, make sure you create a new folder with
the year and month of the "tentative" release.

```{r, echo = FALSE}
decorate("p-dirs") %>% 
  flair("2020_JUL", background = "pink") %>%
  flair("datadir", color = "CornflowerBlue")
```

```{r p-dirs, include=FALSE}
#--------- directories ---------
datadir   <- "p:/01.PovcalNet/02.Production/2020_JUL/"
cpi_path  <- "p:/01.PovcalNet/01.Vintage_control/_aux/price_framework/price_framework.dta"
sheet     <- "SurveyMean"
mdir      <- "p:/01.PovcalNet/00.Master/"
```

### Surveys that have changed {#init-params}

Now, we have to specify what countries/years have been added or changed to the
PovcalNet repository. We recommend you do this country by country.

```{r}
#--------- to modify in each round ---------
countries <- "CHN"
years     <- NULL
```

If you leave the argument `years` equal to `NULL`, the code will update all the
years for the country select. In this case, `r countries`. However, you could
specify what years to update for that particular country, like,

```{r}
countries <- "IND"
years     <- c(1993, 2004, 2009, 2012)
```

It is important to note that *unless you want to update all the years available*
in more than one country, you should not include in the `countries` variable
more than one country.

### Prepare metadata

In the next part we prepare the data. Function `pcn_datafind` finds the
directory path and filenames of the corresponding countries in variable
`countries`. It returns a list with two objects, `fail` and `pcn`. Object `fail`
lets you know if there is any particular data that could not be loaded. Object
`pcn` contains a data frame with the information above.

```{r, eval=FALSE}
#----------------------------------------------------------
#   Generate and Fix metadata
#----------------------------------------------------------
# Find countries
tmp       <- pcn_datafind(country = countries)
pcn_fails <- tmp$fail
pcn       <- as.data.table(tmp$pcn)

# Fix metadata
pcn       <- fix_metadata(pcn)

# Get reference year
pcn       <- get_ref_year(pcn, cpi_path)
```

Then `pcn` object is then passed to the `fix_metadata` function in which some
columns like welfare type of survey coverage are added. Finally, function
`get_ref_year` merges the price framework data from `datalibweb` to assign the
right reference year to each survey. Keep in mind that `get_ref_year` makes some
*hard-coded* adjustments. Check those in case the resulting reference year is
incorrect.

### Generate .pcb files

Now that the metadata is ready, we can create the .pcb file. This is done with
this code,

```{r, eval = FALSE}
# -------------------- Create PCB --------------------
replace_file <- TRUE
pcb_status <- generate_pcb_files(df           = pcn, 
                                 countries    = countries,
                                 years        = years, 
                                 replace_file = replace_file,
                                 datadir      = datadir
```

The function `generate_pcb_files` takes the directory paths of the microdata in
the `pcn` object, loads the microdata, and, inside the `datadir` directory,
creates the .pcb file into the `/01.pcb/` subdirectory and and .rds file (R
readable) into the `/02.rds/` sub-directory. The creation of the .rds is for
convenience. It allows you to check the data in the .pcb in an easy way. The
.pcb file, in contrast, is harder to read directly in R.

One feature of the `generate_pcb_files` functions is that you can add additional
filters by country and year in case you need it. By default, notice that it is
only until this point that the `years` objects defined [above](#init-params) is
being used. In fact, you could create another object, say `countries2`, and
parse it into the argument `countries` of the `generate_pcb_files` function.

Up to this point, the generation of the .pcb files is concluded, but the
PovcalNet system requires two types of inputs, welfare data and the master file.
We still need to update the "SurveyMean" sheet of the Master file.

## Update the Master file

Updating the Master file is the most challenging part of the whole process
because we need to make sure that,

1.  whatever is correct in the master file remains correct.
2.  whatever is wrong is fixed
3.  whatever is not necessary is removed
4.  whatever is missing is added
5.  whatever is duplicated is unified.

Thus, we recommend that you run this sections one by one and check the results
in between. This is specially important for countries with urban/rural coverage
like China, India, or Indonesia; for countries with lagging reference years like
EU-SILC countries, or for tricky countries like ... (Macedonia?).

### Update info of  the "SurveyMean" sheet

The first step is to extract some important metadata information from the .rds
files generated in the previous step. This is done with the following code,

```{r, eval = FALSE}
lf <- update_master_info(df        = pcn, 
                         countries = countries,
                         years     = years)
st  <- lf$s
df <- lf$df

table(st$status)
filter(st, status != "OK")
```

The object `lf` is a list with two objects, `st` and `df`. Object `st` is merely
a status of the previous process, whereas `df` is the actual data.
